Performances Code

### 2019-02-27 Scripts/performances.rmd
added results to performance script

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)

@@

#Evaluating Feature Engineering

@@

>>>>

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)

@@

#Feature Engineering

## Exploring Correlations

train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))

cormat <- cor(binswtad)

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_gm12878_10kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 10, hjust = 1),
       axis.text.y = element_text(size = 10))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_gm12878_10kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_gm12878_10kb) #4595    4
sigcorrs_gm12878_10kb[,3:4] <- round(sigcorrs_gm12878_10kb[,3:4], 4)
sigcorrs_gm12878_10kb <- sigcorrs_gm12878_10kb[order(sigcorrs_gm12878_10kb$pvals, decreasing = FALSE),]

highcorrs_gm12878_10kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_gm12878_10kb) #21  4
highcorrs_gm12878_10kb[,3:4] <- round(highcorrs_gm12878_10kb[,3:4], 2)
highcorrs_gm12878_10kb <- highcorrs_gm12878_10kb[order(abs(highcorrs_gm12878_10kb$value), decreasing = TRUE),]

#clustered heatmap
clustcorplot_gm12878_10kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "Correlation", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(12,9),     # widens margins around plot
          #col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          keysize = 1) 
```

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))

cormat <- cor(binswtad)

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_gm12878_25kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 10, hjust = 1),
       axis.text.y = element_text(size = 10))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_gm12878_25kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_gm12878_25kb) #4683    4
sigcorrs_gm12878_25kb[,3:4] <- round(sigcorrs_gm12878_25kb[,3:4], 4)
sigcorrs_gm12878_25kb <- sigcorrs_gm12878_25kb[order(sigcorrs_gm12878_25kb$pvals, decreasing = FALSE),]

highcorrs_gm12878_25kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_gm12878_25kb) #50  4
highcorrs_gm12878_25kb[,3:4] <- round(highcorrs_gm12878_25kb[,3:4], 2)
highcorrs_gm12878_25kb <- highcorrs_gm12878_25kb[order(abs(highcorrs_gm12878_25kb$value), decreasing = TRUE),]

#clustered heatmap
clustcorplot_gm12878_25kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "Correlation", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          #col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          keysize = 1) 
```

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))

cormat <- cor(binswtad)

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_gm12878_50kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 10, hjust = 1),
       axis.text.y = element_text(size = 10))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_gm12878_50kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_gm12878_50kb) #
sigcorrs_gm12878_50kb[,3:4] <- round(sigcorrs_gm12878_50kb[,3:4], 4)
sigcorrs_gm12878_50kb <- sigcorrs_gm12878_50kb[order(sigcorrs_gm12878_50kb$pvals, decreasing = FALSE),]

highcorrs_gm12878_50kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_gm12878_50kb) #
highcorrs_gm12878_50kb[,3:4] <- round(highcorrs_gm12878_50kb[,3:4], 2)
highcorrs_gm12878_50kb <- highcorrs_gm12878_50kb[order(abs(highcorrs_gm12878_50kb$value), decreasing = TRUE),]

#clustered heatmap
clustcorplot_gm12878_50kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "Correlation", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          #col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          keysize = 1)
```

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))

cormat <- cor(binswtad)

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_gm12878_100kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 10, hjust = 1),
       axis.text.y = element_text(size = 10))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_gm12878_100kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_gm12878_100kb) #4373    4
sigcorrs_gm12878_100kb[,3:4] <- round(sigcorrs_gm12878_100kb[,3:4], 4)
sigcorrs_gm12878_100kb <- sigcorrs_gm12878_100kb[order(sigcorrs_gm12878_100kb$pvals, decreasing = FALSE),]

highcorrs_gm12878_100kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_gm12878_100kb) #424   4
highcorrs_gm12878_100kb[,3:4] <- round(highcorrs_gm12878_100kb[,3:4], 2)
highcorrs_gm12878_100kb <- highcorrs_gm12878_100kb[order(abs(highcorrs_gm12878_100kb$value), decreasing = TRUE),]

#clustered heatmap
clustcorplot_gm12878_100kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "Correlation", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          #col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          keysize = 1)
```

@@

## Evaluating Regularization

### GM12878

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")

features <- names(train)[-1]
features <- features[grep("dist", features)]
features <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "Gm12878", 
                                                    "dist", 
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", features)

#None
##OC
enetcoefs_none_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_none_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_none_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/enetcoefs.rds")

#RUS
##OC
enetcoefs_RUS_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_RUS_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_RUS_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")

#ROS
##OC
enetcoefs_ROS_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_ROS_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_ROS_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")

#SMOTE
##OC
enetcoefs_SMOTE_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_SMOTE_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_SMOTE_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")

enetcoefslist <- list(enetcoefs_none_oc_10kb_gm12878, 
                      enetcoefs_none_op_10kb_gm12878, 
                      enetcoefs_none_dist_10kb_gm12878,
                      enetcoefs_RUS_oc_10kb_gm12878, 
                      enetcoefs_RUS_op_10kb_gm12878, 
                      enetcoefs_RUS_dist_10kb_gm12878,
                      enetcoefs_ROS_oc_10kb_gm12878, 
                      enetcoefs_ROS_op_10kb_gm12878, 
                      enetcoefs_ROS_dist_10kb_gm12878,
                      enetcoefs_SMOTE_oc_10kb_gm12878, 
                      enetcoefs_SMOTE_op_10kb_gm12878, 
                      enetcoefs_SMOTE_dist_10kb_gm12878)

enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})

featuremat_10kb <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
                                                                    "Predictor Type"=rep(c("OC",
                                                                                         "OP", 
                                                                                         "Distance"),4)))

for(j in 1:length(enetcoefslist)){
    featuremat_10kb[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
}

#using lattice
levelplot(t(featuremat_10kb), 
          colorkey=FALSE, 
          scales=list(x=list(rot=45),
                      alternating=3), 
          col.regions=c("white", "red"),
          aspect="fill",panel = function(...){
            panel.levelplot(...)
            panel.abline(v = 3.5);
            panel.abline(v = 6.5);
            panel.abline(v = 9.5);
          },
          xlab="",
          ylab="")
grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))

featuredf <- data.frame(featuremat_10kb)
featuredf$Feature <- rownames(featuredf)
rownames(featuredf) <- NULL
featuredf <- featuredf[,c(13,1:12)]
names(featuredf) <- c("Feature",
                      "None.OC", "None.OP", "None.Distance",
                      "RUS.OC", "RUS.OP", "RUS.Distance",
                      "ROS.OC", "ROS.OP", "ROS.Distance",
                      "SMOTE.OC", "SMOTE.OP", "SMOTE.Distance")

x <- melt(featuredf, id.vars = 1)

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")

features <- names(train)[-1]
features <- features[grep("dist", features)]
features <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "Gm12878", 
                                                    "dist", 
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", features)

#None
##OC
enetcoefs_none_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_none_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_none_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/enetcoefs.rds")

#RUS
##OC
enetcoefs_RUS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_RUS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_RUS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")

#ROS
##OC
enetcoefs_ROS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_ROS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_ROS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")

#SMOTE
##OC
enetcoefs_SMOTE_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_SMOTE_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_SMOTE_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")

enetcoefslist <- list(enetcoefs_none_oc_25kb_gm12878, 
                      enetcoefs_none_op_25kb_gm12878, 
                      enetcoefs_none_dist_25kb_gm12878,
                      enetcoefs_RUS_oc_25kb_gm12878, 
                      enetcoefs_RUS_op_25kb_gm12878, 
                      enetcoefs_RUS_dist_25kb_gm12878,
                      enetcoefs_ROS_oc_25kb_gm12878, 
                      enetcoefs_ROS_op_25kb_gm12878, 
                      enetcoefs_ROS_dist_25kb_gm12878,
                      enetcoefs_SMOTE_oc_25kb_gm12878, 
                      enetcoefs_SMOTE_op_25kb_gm12878, 
                      enetcoefs_SMOTE_dist_25kb_gm12878)

enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})

featuremat_25kb <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
                                                                    "Predictor Type"=rep(c("OC",
                                                                                         "OP", 
                                                                                         "Distance"),4)))

for(j in 1:length(enetcoefslist)){
    featuremat_25kb[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
}

#using lattice
levelplot(t(featuremat_25kb), 
          colorkey=FALSE, 
          scales=list(x=list(rot=45),
                      alternating=3), 
          col.regions=c("white", "red"),
          aspect="fill",panel = function(...){
            panel.levelplot(...)
            panel.abline(v = 3.5);
            panel.abline(v = 6.5);
            panel.abline(v = 9.5);
          },
          xlab="",
          ylab="")
grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))

featuredf <- data.frame(featuremat_25kb)
featuredf$Feature <- rownames(featuredf)
rownames(featuredf) <- NULL
featuredf <- featuredf[,c(13,1:12)]
names(featuredf) <- c("Feature",
                      "None.OC", "None.OP", "None.Distance",
                      "RUS.OC", "RUS.OP", "RUS.Distance",
                      "ROS.OC", "ROS.OP", "ROS.Distance",
                      "SMOTE.OC", "SMOTE.OP", "SMOTE.Distance")

x <- melt(featuredf, id.vars = 1)

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")

features <- names(train)[-1]
features <- features[grep("dist", features)]
features <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "Gm12878", 
                                                    "dist", 
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", features)

#None
##OC
enetcoefs_none_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_none_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_none_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/enetcoefs.rds")

#RUS
##OC
enetcoefs_RUS_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_RUS_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_RUS_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")

#ROS
##OC
enetcoefs_ROS_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_ROS_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_ROS_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")

#SMOTE
##OC
enetcoefs_SMOTE_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_SMOTE_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_SMOTE_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")

enetcoefslist <- list(enetcoefs_none_oc_50kb_gm12878, 
                      enetcoefs_none_op_50kb_gm12878, 
                      enetcoefs_none_dist_50kb_gm12878,
                      enetcoefs_RUS_oc_50kb_gm12878, 
                      enetcoefs_RUS_op_50kb_gm12878, 
                      enetcoefs_RUS_dist_50kb_gm12878,
                      enetcoefs_ROS_oc_50kb_gm12878, 
                      enetcoefs_ROS_op_50kb_gm12878, 
                      enetcoefs_ROS_dist_50kb_gm12878,
                      enetcoefs_SMOTE_oc_50kb_gm12878, 
                      enetcoefs_SMOTE_op_50kb_gm12878, 
                      enetcoefs_SMOTE_dist_50kb_gm12878)

enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})

featuremat_50kb <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
                                                                    "Predictor Type"=rep(c("OC",
                                                                                         "OP", 
                                                                                         "Distance"),4)))

for(j in 1:length(enetcoefslist)){
    featuremat_50kb[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
}

#using lattice
levelplot(t(featuremat_50kb), 
          colorkey=FALSE, 
          scales=list(x=list(rot=45),
                      alternating=3), 
          col.regions=c("white", "red"),
          aspect="fill",panel = function(...){
            panel.levelplot(...)
            panel.abline(v = 3.5);
            panel.abline(v = 6.5);
            panel.abline(v = 9.5);
          },
          xlab="",
          ylab="")
grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))

featuredf <- data.frame(featuremat_50kb)
featuredf$Feature <- rownames(featuredf)
rownames(featuredf) <- NULL
featuredf <- featuredf[,c(13,1:12)]
names(featuredf) <- c("Feature",
                      "None.OC", "None.OP", "None.Distance",
                      "RUS.OC", "RUS.OP", "RUS.Distance",
                      "ROS.OC", "ROS.OP", "ROS.Distance",
                      "SMOTE.OC", "SMOTE.OP", "SMOTE.Distance")

x <- melt(featuredf, id.vars = 1)

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")

features <- names(train)[-1]
features <- features[grep("dist", features)]
features <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "Gm12878", 
                                                    "dist", 
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", features)

#None
##OC
enetcoefs_none_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_none_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_none_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/enetcoefs.rds")

#RUS
##OC
enetcoefs_RUS_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_RUS_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_RUS_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")

#ROS
##OC
enetcoefs_ROS_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_ROS_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_ROS_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")

#SMOTE
##OC
enetcoefs_SMOTE_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_SMOTE_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_SMOTE_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")

enetcoefslist <- list(enetcoefs_none_oc_100kb_gm12878, 
                      enetcoefs_none_op_100kb_gm12878, 
                      enetcoefs_none_dist_100kb_gm12878,
                      enetcoefs_RUS_oc_100kb_gm12878, 
                      enetcoefs_RUS_op_100kb_gm12878, 
                      enetcoefs_RUS_dist_100kb_gm12878,
                      enetcoefs_ROS_oc_100kb_gm12878, 
                      enetcoefs_ROS_op_100kb_gm12878, 
                      enetcoefs_ROS_dist_100kb_gm12878,
                      enetcoefs_SMOTE_oc_100kb_gm12878, 
                      enetcoefs_SMOTE_op_100kb_gm12878, 
                      enetcoefs_SMOTE_dist_100kb_gm12878)
